\textsc{geepers}: Principal Stratification using Principal Scores and Stacked Estimating Equations

### 2022-12-19 writeUps/paper.tex

\begin{figure}[!h]
  \centering
  \includegraphics{../figure/psModCoef.jpg}
  \caption{Principal Score Model Coefficients}
  \label{fig:psMod}
\end{figure}

>>>>

\subsection{Summary Statistics}

\input{table1}

\subsection{Regression Results}
Regression estimates from principal score logit model and three outcome regressions for \textsc{geepers} estimates. Standard errors shown are nominal regression errors, not sandwich corrected. Fixed-effect estimates for school (PS-model) or classroom (outcome models) are omitted.

\input{writeUps/outcomeRegAppendix}
